A decomposition Approach for solving the JSP using multi-shot ASP

### 2022-01-12 Second paper/samplepaper.tex
changed the style

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{helvet,times,courier}
\usepackage{listings}
\usepackage[inline]{enumitem}
\lstset{numberbychapter=false,numbers=left,numberblanklines=false,basicstyle=\footnotesize\ttfamily,xleftmargin=5ex}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{A decomposition Approach for solving the JSP using multi-shot ASP\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Mohammed M. S. El-Kholany\inst{1}\orcidID{0000-0002-1088-2081} \and
Martin Gebser\inst{1,2}\orcidID{0000-0002-8010-4752} \and
Konstantin Schekotihin\inst{1}\orcidID{0000-0002-0286-0958}}
%
\authorrunning{M. El-Kholany et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Alpen-Adria-Universität Klagenfurt, Klagenfurt, Austria 
\email{\{mohammed.el-kholany, martin.gebser and konstantin.schekotihin\}@aau.at}\\
%\url{http://www.springer.com/gp/computer-science/lncs} \and
Technische Universität Graz, Graz, Austria\\
\email{mgebser@ist.tugraz.at}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
150--250 words.

\keywords{Job-shop Scheduling Problem  \and Answer Set Programming \and Decomposition.}
\end{abstract}
%
%
%
\section{Introduction}
In today's competitive markets, manufacturers have to respond quickly to orders and meet shipping dates committed to the customers. This requires the ability to schedule production activities to use the available scarce resources efficiently. Effective scheduling techniques are essential in complex manufacturing systems such as semiconductor manufacturing. In general, scheduling operations is one of the most critical issues in the planning and managing of the manufacturing processes\cite{uzsoy2000performance}.

@@

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\bibliographystyle{splncs04}
\bibliography{Ref}

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass{tlp} % \documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{helvet,times,courier}
\usepackage{listings}
\usepackage[inline]{enumitem}
\lstset{numberbychapter=false,numbers=left,numberblanklines=false,basicstyle=\footnotesize\ttfamily,xleftmargin=5ex}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\newtheorem{theorem}{Theorem}

\begin{document}

\lefttitle{Mohammed M.\ S.\ El-Kholany, Martin Gebser, Konstantin Schekotihin}

\jnlPage{1}{8}
\jnlDoiYr{2021}
\doival{10.1017/xxxxx}

%
\title{A decomposition Approach for solving the JSP using multi-shot ASP}
% \thanks{This work was partially funded by
% KWF project 28472,
% cms electronics GmbH,
% FunderMax GmbH,
% Hirsch Armbänder GmbH,
% incubed IT GmbH,
% Infineon Technologies Austria AG,
% Isovolta AG,
% Kostwein Holding GmbH, and
% Privatstiftung Kärntner Sparkasse.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\begin{authgrp}
\author{\sn{Mohammed M.\ S.} \gn{El-Kholany}} % \inst{1}\orcidID{0000-0002-1088-2081} \and
\affiliation{University of Klagenfurt, Austria \and Cairo University, Egypt}
\author{\sn{Martin} \gn{Gebser}} % \inst{1,2}\orcidID{0000-0002-8010-4752} \and
\affiliation{University of Klagenfurt, Austria \and Graz University of Technology, Austria}
\author{\sn{Konstantin} \gn{Schekotihin}} % \inst{1}\orcidID{0000-0002-0286-0958}
\affiliation{University of Klagenfurt, Austria}
\end{authgrp}
%
%%% \authorrunning{M. El-Kholany et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
%%% \institute{Alpen-Adria-Universität Klagenfurt, Klagenfurt, Austria 
%%% \email{\{mohammed.el-kholany, martin.gebser and konstantin.schekotihin\}@aau.at}\\
%\url{http://www.springer.com/gp/computer-science/lncs} \and
%%% Technische Universität Graz, Graz, Austria\\
%%% \email{mgebser@ist.tugraz.at}}

\history{\sub{xx xx xxxx;} \rev{xx xx xxxx;} \acc{xx xx xxxx}}

\maketitle              % typeset the header of the contribution

\begin{abstract}
The abstract should briefly summarize the contents of the paper in
150--250 words.

% \keywords{Job-shop Scheduling Problem  \and Answer Set Programming \and Decomposition.}
\end{abstract}
%
\begin{keywords}
Job-shop Scheduling Problem, Answer Set Programming, Decomposition
\end{keywords}
%
%
%
\section{Introduction}
In today's competitive markets, manufacturers have to respond quickly to orders and meet shipping dates committed to the customers. This requires the ability to schedule production activities to use the available scarce resources efficiently. Effective scheduling techniques are essential in complex manufacturing systems such as semiconductor manufacturing. In general, scheduling operations is one of the most critical issues in the planning and managing of the manufacturing processes\cite{uzsoy2000performance}.

@@

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\bibliographystyle{tlplike} % \bibliographystyle{splncs04}
\bibliography{Ref}
